RQ2_main

### 2024-12-14 RQ2_final_Sizhe.qmd
Look at RQ2

---
title: "RQ2_main"
format: 
      pdf:
       code-overflow: wrap
editor: visual
---

## Quarto

The `echo: false` option disables the printing of code (only output is displayed).

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,   # Suppress messages
  warning = FALSE    # Suppress warnings
)
```

@@

```{r echo = FALSE, results = FALSE}
file_path <- "//Users/pdeguz01/Documents/git/Data/2020 CMPS/DS0001/39096-0001-Data.rda"

@@

@@

```{r echo=FALSE, results=FALSE}
# Data Cleaning and Recoding for dataset_new
dataset_new <- dataset_new |> 
  mutate(
    # Education recoding
    educ = case_when(
      S13 == "(1) Grades 1-8" ~ "No college experience",
      S13 == "(2) Some High School, but did not graduate" ~ "No college experience",
      S13 == "(3) High School graduate or GED" ~ "No college experience",
      S13 == "(4) Some college" ~ "Some college experience",
      S13 == "(5) Associates, 2-year degree" ~ "College graduate",
      S13 == "(6) Bachelors, 4-year degree" ~ "College graduate",
      S13 == "(7) Post-graduate degree" ~ "College graduate"
    ),
    # Sexual orientation recoding
    sex_orientation = case_when(
      S3 == "(01) Straight, that is, not gay or lesbian" ~ "Straight",
      S3 == "(02) Gay or lesbian" ~ "Queer",
      S3 == "(03) Bisexual" ~ "Queer",
      S3 == "(04) Something else (Specify)" ~ "Queer",
      S3 == "(88) Refused" ~ "Refused/Don't Know",
      S3 == "(99) I don" ~ "Refused/Don't Know"
    ),
    # Urban vs rural recoding
    rural = case_when(
      S14 == "(1) Large urban area" ~ "Urban/suburban",
      S14 == "(2) Large suburb near large city" ~ "Urban/suburban",
      S14 == "(3) Small suburb near small town or city" ~ "Urban/suburban",
      S14 == "(4) Small town or small city" ~ "Urban/suburban",
      S14 == "(5) Rural area" ~ "Rural"
    ),
    # Race recoding
    race_recoded = case_when(
      S2_RACE_PRIME == "(1) White" ~ "White",
      S2_RACE_PRIME == "(2) Hispanic or Latino" ~ "Latino",
      S2_RACE_PRIME == "(3) Black or African American" ~ "Black",
      S2_RACE_PRIME == "(4) Asian American" ~ "Asian American",
      S2_RACE_PRIME == "(5) American Indian/Native American" ~ "AIAN",
      S2_RACE_PRIME == "(6) Arab, Middle Eastern or North African" ~ "Arab/MENA",
      S2_RACE_PRIME == "(7) Native Hawaiian" ~ "NHPI",
      S2_RACE_PRIME == "(8) Not Hawaiian, but other Pacific Islander" ~ "NHPI"
    ),
    # Age recoding
    age_recoded = case_when(
      S5_AGE == "(1) 16-17" ~ "16-17",
      S5_AGE == "(2) 18-29" ~ "18-29",
      S5_AGE == "(3) 30-39" ~ "30-39",
      S5_AGE == "(4) 40-49" ~ "40-49",
      S5_AGE == "(5) 50-59" ~ "50-59",
      S5_AGE == "(6) 60-69" ~ "60-69",
      S5_AGE == "(7) 70 +" ~ "70+"
    )
  ) %>%
  mutate(
    # Converting variables to factors
    race_recoded = factor(race_recoded, levels = c("White", "Black", "Asian American", "Latino", "AIAN", "NHPI", "Arab/MENA")),
    age_recoded = factor(age_recoded, levels = c("18-29", "30-39", "40-49", "50-59", "60-69", "70+")),
    educ = factor(educ, levels = c("No college experience", "Some college experience", "College graduate")),
    rural = factor(rural, levels = c("Rural", "Urban/suburban")),
    sex_orientation = factor(sex_orientation, levels = c("Straight", "Queer", "Refused/Don't Know"))
  )

@@

```{r echo=FALSE, results=FALSE}
# Check the number of missing values for each variable
missing_summary <- sapply(dataset_clean, function(x) sum(is.na(x)))

# Create a data frame to display the missing values clearly
missing_df <- data.frame(Variable = names(missing_summary), Missing_Count = missing_summary)
print(missing_df)

# Extract the variables Q629R1 to Q629R7
racism_vars <- dataset_clean[, grep("^Q629R[1-7]$", names(dataset_clean))]

# Calculate the proportion of missing values for each variable
missing_proportions <- colSums(is.na(racism_vars)) / nrow(racism_vars)

# Convert to a data frame
missing_summary <- data.frame(Variable = names(missing_proportions),
                              Missing_Proportion = round(missing_proportions, 4))

print(missing_summary)
```

@@

# Verify the renamed columns
colnames(dataset_clean)
```

@@

```{r echo=FALSE, results=FALSE}
# Regression model
model <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age +
               Religion,

@@

# Check multicollinearity using VIF
vif(model)
```

## Model 2: stepwise regression
```{r echo=FALSE, results=FALSE}
# Perform stepwise selection
model_stepwise <- step(model, 
                       direction = "both",
                       trace = 0)
```

```{r echo=FALSE, results=FALSE}
# print(model_stepwise)
vif(model_stepwise)
```

```{r echo=FALSE, results=FALSE}

# Extract odds ratios
odds_ratios <- exp(coef(model_stepwise))

# Get confidence intervals for coefficients
conf_intervals <- exp(confint(model_stepwise))

# Extract p-values
p_values <- summary(model_stepwise)$coefficients[, 4]

# Combine everything into a single data frame
results_model_stepwise <- data.frame(
  OddsRatio = odds_ratios,
  LowerCI = conf_intervals[, 1],
  UpperCI = conf_intervals[, 2],
  PValue = p_values
)

# Display results
results_model_stepwise
```

## Model Diagnostics
```{r echo=FALSE, results=FALSE}
# Set seed for reproducibility
set.seed(123)

# Split data into training (70%) and testing (30%)
library(caret)
train_index <- createDataPartition(dataset_clean$ImportanceOfStoppingDiscriminationAgainstMinorities, p = 0.7, list = FALSE)
train_data <- dataset_clean[train_index, ]
test_data <- dataset_clean[-train_index, ]

# Train stepwise logistic regression model on training data

# Fit the initial model (full model)
full_model <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age +
               Religion, 
                  data = train_data, family = "binomial")

# Perform stepwise selection
final_model <- step(full_model, 
                       direction = "both",
                       trace = 0)

# Generate predictions on the test data
predicted_probs <- predict(final_model, newdata = test_data, type = "response")

# Convert probabilities to binary outcomes using a threshold (e.g., 0.5)
predicted_classes <- ifelse(predicted_probs > 0.5, "Important", "Not important")

# Convert predicted classes to factor and align levels with actual classes
predicted_classes <- factor(predicted_classes, levels = c("Not important", "Important"))
actual_classes <- factor(test_data$ImportanceOfStoppingDiscriminationAgainstMinorities, 
                                  levels = c("Not important", "Important"))

# Create confusion matrix
conf_matrix <- confusionMatrix(predicted_classes, actual_classes)

# Print the confusion matrix
print(conf_matrix)
```

```{r echo=FALSE, results=FALSE}
# # Calculate the ROC curve
# roc_curve <- roc(test_data$ImportanceOfStoppingDiscriminationAgainstMinorities, 
#                  predicted_probs_stepwise, 
#                  levels = c("Not important", "Important"))
# 
# # Print the AUC
# auc_value <- auc(roc_curve)
# cat("AUC:", auc_value, "\n")
# 
# # Plot the ROC curve
# plot(roc_curve, col = "blue", main = "ROC Curve")
# abline(a = 0, b = 1, col = "red", lty = 2)  # Add diagonal line for random guess
# 
# # Save the ROC plot
# ggsave("roc_curve_plot.png", width = 8, height = 6)

@@

```{r echo=FALSE}
## Figure 2: 
# Filter for significant variables (p-value < 0.05)
significant_data <- results_model_stepwise[results_model_stepwise$PValue < 0.05, ]

# Add a column for variable names to use in the plot
significant_data <- significant_data %>% 
  mutate(Variable = rownames(significant_data))

# Create the plot
ggplot(significant_data, aes(x = OddsRatio, y = reorder(Variable, OddsRatio))) +
  geom_point(size = 4, color = "blue") +  # Add points for odds ratios
  geom_errorbarh(aes(xmin = LowerCI, xmax = UpperCI), height = 0.3, color = "black") +  # Add horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +  # Add a vertical reference line at Odds Ratio = 1
  labs(
    title = "Significant Variables with Confidence Intervals (Odds Ratio)",
    x = "Odds Ratio",
    y = "Variables"
  ) +
  theme_minimal() +  # Use a minimal theme for better aesthetics
  theme(
    axis.text.y = element_text(size = 6, color = "black"),  # Improve y-axis text readability
    axis.title.x = element_text(size = 12, face = "bold"),  # Highlight x-axis title
    axis.title.y = element_text(size = 12, face = "bold"),  # Highlight y-axis title
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center the title
    plot.margin = margin(1, 1, 1, 1, "cm"),  # Adjust margins
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Reduce x-axis text size
    legend.text = element_text(size = 8),  # Reduce legend text size
    legend.title = element_text(size = 9)  # Reduce legend title size
  )

# Save the plot with larger dimensions
ggsave("Significant_Variables_Plot_Enhanced.png", width = 20, height = 10)
```

## Figure 1: Proportion of outcome variable for RQ 1
```{r echo=FALSE}
# Calculate proportions
proportions <- prop.table(table(dataset$Q1R5))
proportions
# Define custom labels
custom_labels <- c("Not important", "Important")

# Combine custom labels with percentages
pie_labels <- paste(custom_labels, round(proportions * 100, 2), "%")

# Plot the pie chart with custom labels
pie(proportions,
    labels = pie_labels,
    main = "Q1R5: Stopping discrimination against racial/ethnic minorities",
    col = c("lightblue", "salmon"))

ggsave("Proportion_Outcome_variable_RQ2.png", width = 20, height = 10)
```

>>>>

---
title: "RQ2_final"
format: html
editor: visual

execute: 
  warning: false
---

### Loading Libraries

@@

```{r echo = FALSE, results = FALSE}
# Read the dataset
file_path <- "/Users/chensi/Desktop/MIDS/Fall 2024/IDS 702/ICPSR_39096/DS0001/39096-0001-Data.rda"

@@

## Pre-processing Data

@@

```{r echo=FALSE, results=FALSE}
# Data Cleaning and Recoding for dataset_new
# Adding religion column
dataset_new <- dataset_new |> 
  mutate(
    # Education recoding
    educ = case_when(
      S13 == "(1) Grades 1-8" ~ "No college experience",
      S13 == "(2) Some High School, but did not graduate" ~ "No college experience",
      S13 == "(3) High School graduate or GED" ~ "No college experience",
      S13 == "(4) Some college" ~ "Some college experience",
      S13 == "(5) Associates, 2-year degree" ~ "College graduate",
      S13 == "(6) Bachelors, 4-year degree" ~ "College graduate",
      S13 == "(7) Post-graduate degree" ~ "College graduate"
    ),
    # Sexual orientation recoding
    sex_orientation = case_when(
      S3 == "(01) Straight, that is, not gay or lesbian" ~ "Straight",
      S3 == "(02) Gay or lesbian" ~ "Queer",
      S3 == "(03) Bisexual" ~ "Queer",
      S3 == "(04) Something else (Specify)" ~ "Queer",
      S3 == "(88) Refused" ~ "Refused/Don't Know",
      S3 == "(99) I don" ~ "Refused/Don't Know"
    ),
    # Urban vs rural recoding
    rural = case_when(
      S14 == "(1) Large urban area" ~ "Urban/suburban",
      S14 == "(2) Large suburb near large city" ~ "Urban/suburban",
      S14 == "(3) Small suburb near small town or city" ~ "Urban/suburban",
      S14 == "(4) Small town or small city" ~ "Urban/suburban",
      S14 == "(5) Rural area" ~ "Rural"
    ),
    # Race recoding
    race_recoded = case_when(
      S2_RACE_PRIME == "(1) White" ~ "White",
      S2_RACE_PRIME == "(2) Hispanic or Latino" ~ "Latino",
      S2_RACE_PRIME == "(3) Black or African American" ~ "Black",
      S2_RACE_PRIME == "(4) Asian American" ~ "Asian American",
      S2_RACE_PRIME == "(5) American Indian/Native American" ~ "AIAN",
      S2_RACE_PRIME == "(6) Arab, Middle Eastern or North African" ~ "Arab/MENA",
      S2_RACE_PRIME == "(7) Native Hawaiian" ~ "NHPI",
      S2_RACE_PRIME == "(8) Not Hawaiian, but other Pacific Islander" ~ "NHPI"
    ),
    # Age recoding
    age_recoded = case_when(
      S5_AGE == "(1) 16-17" ~ "16-17",
      S5_AGE == "(2) 18-29" ~ "18-29",
      S5_AGE == "(3) 30-39" ~ "30-39",
      S5_AGE == "(4) 40-49" ~ "40-49",
      S5_AGE == "(5) 50-59" ~ "50-59",
      S5_AGE == "(6) 60-69" ~ "60-69",
      S5_AGE == "(7) 70 +" ~ "70+"
    )
  ) |>
  mutate(
    # Converting variables to factors
    race_recoded = factor(race_recoded, levels = c("White", "Black", "Asian American", "Latino", "AIAN", "NHPI", "Arab/MENA")),
    age_recoded = factor(age_recoded, levels = c("18-29", "30-39", "40-49", "50-59", "60-69", "70+")),
    educ = factor(educ, levels = c("No college experience", "Some college experience", "College graduate")),
    rural = factor(rural, levels = c("Rural", "Urban/suburban")),
    sex_orientation = factor(sex_orientation, levels = c("Straight", "Queer", "Refused/Don't Know"))
  )

@@

@@

# Verify the renamed columns
colnames(dataset_clean)
head(dataset_clean)
```

@@

## Model 1: Main

```{r echo=FALSE, results=FALSE}
# Regression model
base_model <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age,

@@

# Check multicollinearity using VIF
vif(base_model)
```

## Model 2: Model with interaction term

```{r echo=FALSE, results=FALSE}
interaction_model <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ 
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Age + 
                 Gender * Race,

# Check multicollinearity using VIF
vif(interaction_model)
```

# Selecting the better model

## Calculating model's goodness-of-fit through deviance and chi-square test

```{r}
anova(base_model, interaction_model, test="Chisq")
```

# confusion matrix

```{r}
# Generate predicted probabilities and binary predictions
predicted_probs <- predict(base_model, type = "response")

# Generate binary predictions with a threshold of 0.5
predicted_classes <- ifelse(predicted_probs > 0.5, 1, 0)

# Create a confusion matrix
confusion_matrix <- table(
  Actual = dataset_clean$ImportanceOfStoppingDiscriminationAgainstMinorities,
  Predicted = predicted_classes
)
print("Confusion Matrix:")
print(confusion_matrix)

# Calculate metrics from the confusion matrix
TP <- confusion_matrix[2, 2]  # True Positives
TN <- confusion_matrix[1, 1]  # True Negatives
FP <- confusion_matrix[1, 2]  # False Positives
FN <- confusion_matrix[2, 1]  # False Negatives

# Compute performance metrics
accuracy <- (TP + TN) / sum(confusion_matrix)
precision <- TP / (TP + FP)
recall <- TP / (TP + FN)
specificity <- TN / (TN + FP)
f1_score <- 2 * (precision * recall) / (precision + recall)

cat("Metrics:\n")
cat(sprintf("Accuracy: %.4f\n", accuracy))
cat(sprintf("Precision: %.4f\n", precision))
cat(sprintf("Recall (Sensitivity): %.4f\n", recall))
cat(sprintf("Specificity: %.4f\n", specificity))
cat(sprintf("F1-Score: %.4f\n", f1_score))

@@

The model performs well for the majority class ("Not important") but struggles significantly with the minority class ("Important"), as shown by the low recall and F1-Score.

-   **Imbalance in Recognizing Importance**:

    -   The model has high specificity (94.86%), meaning it effectively identifies respondents who do **not** place high importance on anti-discrimination policies.

    -   However, the low sensitivity (15.63%) shows the model struggles to identify respondents who do place high importance on such policies.

    -   This could suggest a possible imbalance in how different factors (e.g., experiences with racism, demographics) are weighed in the model, potentially requiring better feature selection or adjustments.

-   **Predictive Power of the Model**:

    -   The moderate accuracy (74.48%) suggests the model provides a reasonable prediction of respondents' views, but the low F1-Score (23.97%) indicates that it has difficulty capturing nuanced relationships, especially for respondents who prioritize such policies.

    -   This highlights a need for deeper exploration into how experiences of racism interact with demographic factors to influence policy importance.

# ROC

```{r}
# ROC Curve
library(pROC)
roc_curve <- roc(dataset_clean$ImportanceOfStoppingDiscriminationAgainstMinorities, predicted_probs)
plot(roc_curve, main = "ROC Curve", col = "blue", lwd = 2)
auc_value <- auc(roc_curve)
cat(sprintf("AUC: %.4f\n", auc_value))
```

The ROC curve confirms that the model has discriminatory power but could be improved, particularly in recognizing minority class cases.

-   **Moderate Discriminatory Power**:

    -   The ROC curve and AUC suggest the model moderately distinguishes between respondents who place high vs. low importance on policies addressing racial discrimination.

    -   This could mean that personal experiences with racism and demographic factors do play a role but may not fully account for the variance in the outcome.

-   **Potential for Model Improvement**:

    -   The curve indicates room for improvement in how the model uses predictors. For example, interactions between demographic factors (e.g., education and race) and personal experiences with racism might enhance predictive accuracy.

### 2024-12-14 RQ2_main copy.qmd
Look at RQ2

```{r echo = FALSE, results = FALSE}
file_path <- "/Users/nakiyahdhariwala/StatsProject/39096-0001-Data.rda"

@@

@@

```{r echo=FALSE, results=FALSE}
# Regression model
model <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age +
               Religion,

@@

## Model 2: stepwise regression
```{r echo=FALSE, results=FALSE}
# Perform stepwise selection
model_stepwise <- step(model, 
                       direction = "both",
                       trace = 0)
```

```{r echo=FALSE, results=FALSE}
# print(model_stepwise)
vif(model_stepwise)
```

@@

# Extract odds ratios
odds_ratios <- exp(coef(model_stepwise))

# Get confidence intervals for coefficients
conf_intervals <- exp(confint(model_stepwise))

# Extract p-values
p_values <- summary(model_stepwise)$coefficients[, 4]

# Combine everything into a single data frame
results_model_stepwise <- data.frame(
  OddsRatio = odds_ratios,
  LowerCI = conf_intervals[, 1],
  UpperCI = conf_intervals[, 2],
  PValue = p_values
)

# Display results
results_model_stepwise
```

## Model Diagnostics
```{r echo=FALSE, results=FALSE}
# Set seed for reproducibility
set.seed(123)

@@

## Figure 1: Proportion of outcome variable for RQ 1
```{r echo=FALSE}
# Calculate proportions
proportions <- prop.table(table(dataset$Q1R5))
proportions
# Define custom labels
custom_labels <- c("Not important", "Important")

>>>>

```{r echo = FALSE, results = FALSE}
file_path <- "39096-0001-Data.rda"

@@

```{r}
head(dataset_clean)
```

@@

## Model 1: Main
```{r echo=FALSE, results=FALSE}
# Regression model
model <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age +
               Religion,

@@

```{r}
# Extract odds ratios
odds_ratios <- exp(coef(model))

# Get confidence intervals for coefficients
conf_intervals <- exp(confint(model))

# Extract p-values
p_values <- summary(model)$coefficients[, 4]

# Combine everything into a single data frame
results_model <- data.frame(
  OddsRatio = odds_ratios,
  LowerCI = conf_intervals[, 1],
  UpperCI = conf_intervals[, 2],
  PValue = p_values
)

# Display results
results_model
```

## Model 2: Without Religion
```{r echo=FALSE, results=FALSE}
model_without_religion <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age,

# Check multicollinearity using VIF
vif(model_without_religion)
```

@@

# Extract odds ratios
odds_ratios <- exp(coef(model_without_religion))

# Get confidence intervals for coefficients
conf_intervals <- exp(confint(model_without_religion))

# Extract p-values
p_values <- summary(model_without_religion)$coefficients[, 4]

# Combine everything into a single data frame
results_model_without_religion <- data.frame(
  OddsRatio = odds_ratios,
  LowerCI = conf_intervals[, 1],
  UpperCI = conf_intervals[, 2],
  PValue = p_values
)

# Display results
results_model_without_religion
```

## Model 3: Model without religion + interaction term
```{r echo=FALSE, results=FALSE}
model_noreligion_Interaction <- glm(ImportanceOfStoppingDiscriminationAgainstMinorities ~ Gender +
               TreatedUnfairlyOrDiscriminatedAgainst + 
               DiscriminationImpactOnLifeSatisfaction +
               PerceptionsOfDiscriminationAgainstWhites + 
               PerceptionsOfDiscriminationAgainstBlacks +
               PerceptionsOfDiscriminationAgainstAsianAmericans + 
               PerceptionsOfDiscriminationAgainstNativeAmericans + 
               PerceptionsOfDiscriminationAgainstImmigrants + 
               PerceptionsOfDiscriminationAgainstLatinos + 
               PerceptionsOfDiscriminationAgainstGaysAndLesbians + 
               PerceptionsOfDiscriminationAgainstMuslims +
               Education + 
                 SexOrientation +
                 Rural +
                 Race +
                 Age + 
                 Gender * Race,

# Check multicollinearity using VIF
vif(model_noreligion_Interaction)
```

# Extract odds ratios
odds_ratios <- exp(coef(model_noreligion_Interaction))

# Get confidence intervals for coefficients
conf_intervals <- exp(confint(model_noreligion_Interaction))

# Extract p-values
p_values <- summary(model_noreligion_Interaction)$coefficients[, 4]

# Combine everything into a single data frame
results_model_noreligion_Interaction <- data.frame(
  OddsRatio = odds_ratios,
  LowerCI = conf_intervals[, 1],
  UpperCI = conf_intervals[, 2],
  PValue = p_values
)

# Display results
model_noreligion_Interaction
```

```{r}
results_model_noreligion_Interaction
```

```{r}
model_noreligion_Interaction
model_without_religion

anova(model_without_religion, model_noreligion_Interaction, test="Chisq")

```{r}
results_model_noreligion_Interaction
```

# Model Diagnostics

```{r}
# Convert the prediction to a factor with correct levels
model_prediction_factor <- factor(model_prediction, 
                                  levels = c(0, 1), 
                                  labels = c("Important", "Not important"))

# Convert the response variable to a factor with matching levels
response_factor <- factor(dataset_clean$ImportanceOfStoppingDiscriminationAgainstMinorities,
                          levels = c("Important", "Not important"))

# Generate the confusion matrix
confusionMatrix(table(model_prediction_factor, response_factor),
                positive = "Important",
                mode = "everything")
```

## OLD DATA

```{r echo=FALSE, results=FALSE}
# Set seed for reproducibility
set.seed(123)

@@

## Figure 1: Proportion of outcome variable for RQ 1

```{r echo=FALSE}
# Calculate proportions
proportions <- prop.table(table(dataset$Q1R5))
proportions
# Define custom labels
custom_labels <- c("Not important", "Important")

### 2024-12-14 RQ2_main.qmd
Look at RQ2

## Model 2: stepwise regression
```{r echo=FALSE, results=FALSE}
# Perform stepwise selection
model_stepwise <- step(model, 
                       direction = "both",
                       trace = 0)
```

@@

## Model Diagnostics
```{r echo=FALSE, results=FALSE}
# Set seed for reproducibility
set.seed(123)

>>>>

## Model 2: stepwise regression

```{r echo=FALSE, results=FALSE}
# Perform stepwise selection
model_stepwise <- step(model, 
                       direction = "both",
                       trace = 0)
```

@@

## Model Diagnostics

```{r echo=FALSE, results=FALSE}
# Set seed for reproducibility
set.seed(123)
